---
title: "Lab1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4793LABStayl0048)
```
[Package Making](https://r-pkgs.org/vignettes.html)


#Latex Formulas

$\bar{x}_k=\frac{1}{n}\sum_{j=1}^{n}x_{jk}$

$s_{ik}=\frac{1}{n}*\sum_{j=1}^{n}(x_{ji}-\bar{x}_{i})(x_{jk}-\bar{x}_{k})$

$r_{ik}=\frac{s_{ik}}{\sqrt{s_{ii}}\sqrt{s_{kk}}}=\frac{\sum_{j=1}^{n}(x_{ji}-\bar{x}_{i})(x_{jk}-\bar{x}_{k})}{\sqrt{{\sum_{j=1}^{n}(x_{ji}-\bar{x}_{i})^2}\sum_{j=1}^{n}(x_{jk}-\bar{x}_{k})^2}}$

$\textbf{S}=\frac{1}{n-1}\textbf{X}^{'}(\textbf{I}-\frac{1}{n}\textbf{I I}^{'})\textbf{X}$

$$
	\textbf{R}=\begin{bmatrix} 
	\frac{s_{11}}{\sqrt{s_{11}}\sqrt{s_{11}}} & \frac{s_{12}}{\sqrt{s_{11}}\sqrt{s_{22}}} & . . . & \frac{s_{1p}}{\sqrt{s_{11}}\sqrt{s_{pp}}} \\
	. . . & . . . & . . .\\
		\frac{s_{1p}}{\sqrt{s_{11}}\sqrt{s_{pp}}} & \frac{s_{2p}}{\sqrt{s_{22}}\sqrt{s_{pp}}} & . . . & \frac{s_{pp}}{\sqrt{s_{pp}}\sqrt{s_{pp}}} \\
	\end{bmatrix}=\begin{bmatrix} 
	1 & r_{12} & ... & r_{1p} \\
	... & ... & ... &...\\
	r_{1p} & r_{2p} & ... & 1 \\
	\end{bmatrix}
	\quad
	\quad
$$
# Examples

```{r}
x=read.table("T1-2.DAT", 
           header=TRUE)
```

```{r}

```

```{r}
ArrayMean(x)
BiasedCovariance(2, 3)
```
# Course Assessment

## In-class quiz each class and lab 
## 4 Assignments (20% Total)
## Laboratories (10% Total)
## 2 exams (10% each, Total 20%)
## 2 Projects, Total 10%
## 1 Final, 30%
